Emissions and Perceptions of Climate Change

### 2022-12-06 Code/Drafts/Final_Short_Oral_Presentation.Rmd
Transfering Diverging bar and chi squared to Final version

```
```{r}
fuels_diverging <- fuels %>% mutate(percent=if_else(response %in% c("Much less", "Somewhat less"), Number, -Number)) 
#everything in there 
```

@@

```{r}
ugh<- survey %>% filter()
```

```{r}
fuels_numPeople<-fuels_numPeople %>% filter(response != "Don't know") #excluding don't know

fuels_numPeople$grouped_answer<- NA
more<- which( fuels_numPeople$response== "Much less" |fuels_numPeople$response== "Somewhat less" )
less<- which( fuels_numPeople$response== "Much more" |fuels_numPeople$response== "Somewhat more" | fuels_numPeople$response== "Refused" |fuels_numPeople$response== "Same amount as today")

  fuels_numPeople$grouped_answer[more]<- "more"
  fuels_numPeople$grouped_answer[less]<- "less"

fuels_numPeople<- fuels_numPeople %>% group_by(Country, grouped_answer) %>% summarise(grouped_number=sum(total))

fuels_numPeople<- fuels_numPeople %>% filter(grouped_answer != is.na)
```

>>>>

```{r}
fuels_diverging <- fuels %>% mutate(percent=if_else(response %in% c("Much less", "Somewhat less"), Number, -Number)) 
#everything in there 
```

@@
